---
title: "Hulpmiddelen onderzoek/analyse"
author: "Jesse Postma"
date: "`r Sys.Date()`"
output: html_document
bibliography: references_hulp.bib
---

```{r, eval=T, echo=F}
library(gt)
```

Dit document bevat hulpmiddelen en hun bronnen gebruikt in het onderzoek.

## Library list

```{r eval=F, echo=F, include=F}
tabel_lib <- tribble(
  ~"Library", ~"Versie", ~"Gebruiksdoel",
  "tidyverse", "2.0.0", "Filteren & sorteren van de data.",
  "ggplot2", "4.0.3", "Produceren van grafieken.",
  "tidyr", "1.3.2", "Creëren van tidy data.",
  "dplyr", "1.2.1", "Muteren van dataframes.",
  "effectsize", "1.0.2", "Verkrijgen van effectsize voor analyse.",
  "flextable", "0.9.11", "Exporteren dataframes naar png.",
  "mirt", "1.46.1", "Implementatie Item Response Theory."
  )

tabel_lib %>%
  gt() %>%
  tab_header(
    title = "Gebruikte libraries",
    subtitle = "Versie, en gebruiksdoel"
  ) %>%
  gtsave("tabel_lib.html")
```

## Shapiro-Wilk information:

Via: [@Shapiro-Wilk] When to Use the Shapiro-Wilk Normality Test

- You want to test whether your data follow a normal distribution.
- Your sample size is relatively small (commonly used for n \< 50, but valid up to around 2,000 observations).
- You’re planning to use statistical methods that assume normality, such as t-tests or ANOVA.

To perform a Shapiro-Wilk normality test, use my free online Normality Test Calculator! Interpreting the Results

The null hypothesis of the Shapiro-Wilk normality test is that the data are a random sample that was drawn population that follows a normal distribution.

- High p-value (p \> 0.05): Fail to reject the null hypothesis. The data do not significantly deviate from normality.
- Low p-value (p ≤ 0.05): Reject the null hypothesis. The data significantly deviate from normality.

## Cohens_d

Via: [Cohens_d] Using this formula, here is how we interpret Cohen’s d:

- A d of 0.5 indicates that the two group means differ by 0.5 standard deviations.
- A d of 1 indicates that the group means differ by 1 standard deviation.
- A d of 2 indicates that the group means differ by 2 standard deviations.

Cohen’s d Percentage of Group 2 who would be below average person in Group 1

| Cohens d | Percentage of Group 2 who would be below average person in Group 1 |
|----|----|
| 0.0 | 50% |
| 0.2 | 58% |
| 0.4 | 66% |
| 0.6 | 73% |
| 0.8 | 79% |
| 1.0 | 84% |


---

<table class="gt_table" data-quarto-disable-processing="false" data-quarto-bootstrap="false">
  <thead>
    <tr class="gt_heading">
      <td colspan="3" class="gt_heading gt_title gt_font_normal" style>Gebruikte libraries</td>
    </tr>
    <tr class="gt_heading">
      <td colspan="3" class="gt_heading gt_subtitle gt_font_normal gt_bottom_border" style>Versie, en gebruiksdoel</td>
    </tr>
    <tr class="gt_col_headings">
      <th class="gt_col_heading gt_columns_bottom_border gt_left" rowspan="1" colspan="1" scope="col" id="Library">Library</th>
      <th class="gt_col_heading gt_columns_bottom_border gt_right" rowspan="1" colspan="1" scope="col" id="Versie">Versie</th>
      <th class="gt_col_heading gt_columns_bottom_border gt_left" rowspan="1" colspan="1" scope="col" id="Gebruiksdoel">Gebruiksdoel</th>
    </tr>
  </thead>
  <tbody class="gt_table_body">
    <tr><td headers="Library" class="gt_row gt_left">tidyverse</td>
<td headers="Versie" class="gt_row gt_right">2.0.0</td>
<td headers="Gebruiksdoel" class="gt_row gt_left">Filteren &amp; sorteren van de data.</td></tr>
    <tr><td headers="Library" class="gt_row gt_left">ggplot2</td>
<td headers="Versie" class="gt_row gt_right">4.0.3</td>
<td headers="Gebruiksdoel" class="gt_row gt_left">Produceren van grafieken.</td></tr>
    <tr><td headers="Library" class="gt_row gt_left">tidyr</td>
<td headers="Versie" class="gt_row gt_right">1.3.2</td>
<td headers="Gebruiksdoel" class="gt_row gt_left">Creëren van tidy data.</td></tr>
    <tr><td headers="Library" class="gt_row gt_left">dplyr</td>
<td headers="Versie" class="gt_row gt_right">1.2.1</td>
<td headers="Gebruiksdoel" class="gt_row gt_left">Muteren van dataframes.</td></tr>
    <tr><td headers="Library" class="gt_row gt_left">effectsize</td>
<td headers="Versie" class="gt_row gt_right">1.0.2</td>
<td headers="Gebruiksdoel" class="gt_row gt_left">Verkrijgen van effectsize voor analyse.</td></tr>
    <tr><td headers="Library" class="gt_row gt_left">flextable</td>
<td headers="Versie" class="gt_row gt_right">0.9.11</td>
<td headers="Gebruiksdoel" class="gt_row gt_left">Exporteren dataframes naar png.</td></tr>
    <tr><td headers="Library" class="gt_row gt_left">mirt</td>
<td headers="Versie" class="gt_row gt_right">1.46.1</td>
<td headers="Gebruiksdoel" class="gt_row gt_left">Implementatie Item Response Theory.</td></tr>
  </tbody>
  
</table>
