---
title: "Hulpmiddelen onderzoek/analyse"
author: "Jesse Postma"
date: "`r Sys.Date()`"
output: html_document
bibliography: references_hulp.bib
---

```{r, eval=T, echo=F}
library(gt)
```

Dit document bevat hulpmiddelen en hun bronnen gebruikt in het onderzoek.

## Library list

```{r eval=F, echo=F, include=F}
tabel_lib <- tribble(
  ~"Library", ~"Versie", ~"Gebruiksdoel",
  "tidyverse", "2.0.0", "Filteren & sorteren van de data.",
  "ggplot2", "4.0.3", "Produceren van grafieken.",
  "tidyr", "1.3.2", "Creëren van tidy data.",
  "dplyr", "1.2.1", "Muteren van dataframes.",
  "effectsize", "1.0.2", "Verkrijgen van effectsize voor analyse.",
  "flextable", "0.9.11", "Exporteren dataframes naar png.",
  "mirt", "1.46.1", "Implementatie Item Response Theory."
  )

tabel_lib %>%
  gt() %>%
  tab_header(
    title = "Gebruikte libraries",
    subtitle = "Versie, en gebruiksdoel"
  ) %>%
  gtsave("tabel_lib.html")
```

## Shapiro-Wilk information:

Via: [@Shapiro-Wilk] When to Use the Shapiro-Wilk Normality Test

- You want to test whether your data follow a normal distribution.
- Your sample size is relatively small (commonly used for n \< 50, but valid up to around 2,000 observations).
- You’re planning to use statistical methods that assume normality, such as t-tests or ANOVA.

To perform a Shapiro-Wilk normality test, use my free online Normality Test Calculator! Interpreting the Results

The null hypothesis of the Shapiro-Wilk normality test is that the data are a random sample that was drawn population that follows a normal distribution.

- High p-value (p \> 0.05): Fail to reject the null hypothesis. The data do not significantly deviate from normality.
- Low p-value (p ≤ 0.05): Reject the null hypothesis. The data significantly deviate from normality.

## Cohens_d

Via: [@Cohens_d] Using this formula, here is how we interpret Cohen’s d:

- A d of 0.5 indicates that the two group means differ by 0.5 standard deviations.
- A d of 1 indicates that the group means differ by 1 standard deviation.
- A d of 2 indicates that the group means differ by 2 standard deviations.

Cohen’s d Percentage of Group 2 who would be below average person in Group 1

| Cohens d | Percentage of Group 2 who would be below average person in Group 1 |
|----|----|
| 0.0 | 50% |
| 0.2 | 58% |
| 0.4 | 66% |
| 0.6 | 73% |
| 0.8 | 79% |
| 1.0 | 84% |


---

## VIF

Via [@VIF]
Variance Inflation Factors (VIFs) measure the correlation among independent variables in least squares regression models. Statisticians refer to this type of correlation as multicollinearity. Excessive multicollinearity can cause problems for regression models.

How High is Too High?

A moderate amount of multicollinearity is okay. However, as multicollinearity increases, its effects also increase. What VIF values represent too much correlation?

I’ve seen different thresholds. I consider VIFs of five and higher to represent problematic amounts of multicollinearity. However, I’ve seen recommendations range from 2.5 to 10! I wish I could give you a concrete answer. However, I’ve long used five as a threshold, and that seems to work well.

Another consideration is that each coefficient estimate has its own standard error with its corresponding VIF. Consequently, you should evaluate each independent variable separately for multicollinearity. Even when some IVs in your model have high VIFs, other variables might have low VIFs and be absolutely fine. When extreme multicollinearity is present in some variables, it does not affect IVs with low VIFs.

## Logistic model interpretation

Via [@Logm]
